Enhanced proximity effect in zigzag-shaped Majorana Josephson junctions.

### 2019-02-23 paper/snakemajoranas.tex
write fig 1 caption

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{figures/zigzag.pdf}
\caption{Setups. Figure of a straight and zigzag system, including trajectories.
\label{fig:setup}}
\end{figure}

>>>>

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{figures/zigzag.pdf}
\caption{Setup of the straight (top) and the zigzag (bottom) SNS junction.
The yellow areas are the superconductors at a phase difference $\pm \phi / 2$.
The middle area is the semiconductor of width $W$ and has a magnetic field $B$ in the $x$-direction.
The modulation of the zigzag is parameterized by its amplitude $z_y$ and period $z_x$.
Inside the semiconductor we indicate the longest possible trajectory by the red wiggly line.
\label{fig:setup}}
\end{figure}
